Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-26 manuscript.Rmd
Fix typo
Add error bars to daily cohesion plot

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_word
#output            : papaja::apa6_pdf
---

@@

Related previous work has also explored diffusion of hashtags in viral contagion in
Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
[@fink2016complex]. The prevalence and rate of particular hashtags were
contributed to the overall sociolinguistic cohesion. The more that people
reuse hashtags or common phrases, the greater the sociolinguistic cohesion when
this phenomenon occurs during socially significant times like protests
[@state2015diffusion].

@@

# read in social cohesion data
cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")

# plot time series
raw_cohesion_ts <- ggplot(cohesion_df, aes(x= as.Date(Date), y=MeanCohesion)) +
  geom_point() +
  geom_line() +
  #geom_errorbar(aes(ymin=len-ci, ymax=len+ci), colour="black", width=.1, position=pd) +
  xlab("Date") +
  ylab("Mean Social Cohesion")
ggsave("./results/primary/raw-cohesion-ts.png")

>>>>

documentclass     : "apa6"
classoption       : "man"
#output            : papaja::apa6_word
output            : papaja::apa6_pdf
---

@@

Related previous work has also explored diffusion of hashtags in viral contagion in
Nigeria, a phenomenon similar to what we identify as sociolinguistic cohesion
[@fink2016complex]. The prevalence and rate of particular hashtags
contributed to the overall sociolinguistic cohesion. The more that people
reuse hashtags or common phrases, the greater the sociolinguistic cohesion when
this phenomenon occurs during socially significant times like protests
[@state2015diffusion].

@@

# read in social cohesion data
#cohesion_df <- read.csv("./data/formatted/primary/formatted_data.csv")
raw_cohesion_data <- read.csv("./data/raw/syria_cohesion.csv")

# converge date to single variable
raw_cohesion_data$Start.Year <- "2012"
raw_cohesion_data$date <- as.Date(with(raw_cohesion_data,
                                       paste(Start.Year, Start.Month, Start.Day,
                                            sep="-")), "%Y-%m-%d")

# detach plyr so summarise works
detach("package:plyr", unload=TRUE)

# calculate mean cohesion
raw_cohesion_data %>%
  group_by(date) %>%
  summarise(
    MeanCohesion = mean(Cohesion_avg),
    sd = sd(Cohesion_avg),
    var = sd^2,
    n = n(),
    se = sd / n) %>%
  ggplot(aes(x = date, y = MeanCohesion)) +
  geom_errorbar(aes(ymin = MeanCohesion-var, ymax = MeanCohesion+var), color = "grey57") +
  geom_point() +
  geom_line() +
  xlab("Date") +
  ylab("Mean Social Cohesion")
